|

### 2023-07-18 paper/03-methods.Rmd
Changed "dimension" to "unit"
Changes "second" to "seconds"

In materials science, strain [@callister2018materials] is the deformation of a material from stress, showing the change in a material's length relative to its original length.
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The strain for a material at time $t$ is defined as 
\begin{equation*}
\varepsilon(t)= \frac{L(t) - L_{0}}{L_{0}}.
\end{equation*}
Notice that this measure is unitless due to being a ratio of two quantities having the same dimension.

Accordingly, the strain rate of a material measures the change in its deformation with respect to time.
Mathematically, the strain rate of a material can be expressed as the derivative of its strain.
That is,
\begin{equation*}
\varepsilon'(t) = \frac{d \varepsilon}{dt} = \frac{v(t)}{L_{0}},
\end{equation*}
where $v(t)$ is the velocity at which the two points of interest within the material are moving away from or towards each other.
Whereas strain has no units, the strain rate is measured in inverse of time, usually 1/second.

>>>>

In materials science, strain [@callister2018materials] is the deformation of a material from stress, showing the change in a material's length relative to its original length.
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The strain for a material at time $t$ is defined as 
\begin{equation*}
\varepsilon(t)= \frac{L(t) - L_{0}}{L_{0}}.
\end{equation*}
Notice that this measure is unitless due to being a ratio of two quantities having the same units.

Accordingly, the strain rate of a material measures the change in its deformation with respect to time.
Mathematically, the strain rate of a material can be expressed as the derivative of its strain.
That is,
\begin{equation*}
\varepsilon'(t) = \frac{d \varepsilon}{dt} = \frac{v(t)}{L_{0}},
\end{equation*}
where $v(t)$ is the velocity at which the two points of interest within the material are moving away from or towards each other.
Whereas strain has no units, the strain rate is measured in inverse of time, usually 1/seconds.
